### 2019-02-08 3-Appendices/1-Appendix/appendix1.tex
Better outline

%!TEX root = ../thesis.tex
% ******************************* Thesis Appendix A ****************************
\chapter{Appendix for Chapter \ref{chapter:1}}
\label{app:chapt1}

@@

>>>>

%!TEX root = ../thesis.tex
% ******************************* Thesis Appendix A ****************************
\chapter{Mathematical Tools}
\label{app:1:mathsTools}

@@

% ----------------------------------------------------------------------------
\section{Concentration Inequalities}
\label{sec:app1:ConcentrationInequalities}

I probably need to include Hoeffding's inequality, Chernoff's method etc.

Reference: [Boucheron et al], [?]

% ----------------------------------------------------------------------------
\section{Useful lemmas}
\label{sec:app1:UsefulLemmas}

I probably need to include a bunch of useful lemmas, used in various places in the thesis, like Pinkser's inequality, etc.

% ----------------------------------------------------------------------------
\section{Results about klUCB}
\label{sec:app1:resultsklUCB}

I probably need to include some results about klUCB, mainly coming from the journal [Garivier et al], used in various places in the thesis.

### 2019-02-08 3-Appendices/2-Appendix/appendix2.tex
Better outline

%!TEX root = ../thesis.tex
% ******************************* Thesis Appendix B ****************************
\chapter{Appendix for Chapter \ref{chapter:2}}
\label{app:chapt2}

In this appendix, blabla.

>>>>

%!TEX root = ../thesis.tex
% ******************************* Thesis Appendix B ****************************
\chapter{Publication: What Doubling-Trick Can and Can't Do for Multi-Armed Bandits}
\label{app:2:DoublingTricks}

See https://hal.inria.fr/hal-01736357

I cannot include it raw without more work on the maths, Emilie wants to write only the best versions of our results.

But I am interested in including this article in my thesis, mainly because GLRklUCB in Chapter 6 is not anytime!

I need to try DoublingTrick + GLRklUCB, at least experimentally!
For the theoretical analysis, it will probably be a huge failure.
